A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-28 main.Rmd
Section 2.2

@wickham2014tidy coined the term "tidy data", which is a rephrasing of the second and third normal forms in relational databases but in a way that makes more sense to data scientists by referring rows to observations and columns to variables. The principles of "tidy data" attempt to standardize the mapping of the semantics of a dataset to its physical representation. This data structure is the fundamental unit of the **tidyverse**, which is a collection of R packages designed for data science. The ubiquitous use of **tidyverse** is testament to the simplicity, practicality and general applicability of the tools. The **tidyverse** provides abstract yet functional grammars to manipulate and visualize data in easier-to-comprehend form. One of the **tidyverse** packages, **dplyr** [@R-dplyr] showcases the value of a grammar as a principled vehicle to transform data for a wide range of data challenges, providing a consistent set of verbs: `mutate()`, `select()`, `filter()`, `summarise()`, and `arrange()`. Each verb focuses on a singular task. Most common data tasks can be rephrased and tackled with these five key verbs, by composing them sequentially.

>>>>

@wickham2014tidy coined the term "tidy data", which is a rephrasing of the second and third normal forms in relational databases but in a way that makes more sense to data scientists by referring rows to observations and columns to variables. The principles of "tidy data" attempt to standardize the mapping of the semantics of a dataset to its physical representation. This data structure is the fundamental unit of the **tidyverse**, which is a collection of R packages designed for data science. The ubiquitous use of the **tidyverse** is testament to the simplicity, practicality and general applicability of the tools. The **tidyverse** provides abstract yet functional grammars to manipulate and visualize data in easier-to-comprehend form. One of the **tidyverse** packages, **dplyr** [@R-dplyr], showcases the value of a grammar as a principled vehicle to transform data for a wide range of data challenges, providing a consistent set of verbs: `mutate()`, `select()`, `filter()`, `summarize()`, and `arrange()`. Each verb focuses on a singular task. Most common data tasks can be rephrased and tackled with these five key verbs, by composing them sequentially.
